---
author: Your Name (Student ID)
date: "`r Sys.Date()`"
output: html_document
title: COMPXXXX Assignment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse) 
library(kableExtra)
```
By including this statement, we the authors of this work, verify that:

- We hold a copy of this assignment that we can produce if the original is lost or
damaged.
- We hereby certify that no part of this assignment/product has been copied from
any other student’s work or from any other source except where due acknowledgement
is made in the assignment.
- No part of this assignment/product has been written/produced for us by another
person except where such collaboration has been authorised by the subject lecturer/
tutor concerned.
- We are aware that this work may be reproduced and submitted to plagiarism detection
software programs for the purpose of detecting possible plagiarism (which
may retain a copy on its database for future plagiarism checking).
- We hereby certify that we have read and understand what the School of Computing,
Engineering and Mathematics defines as minor and substantial breaches
of misconduct as outlined in the learning guide for this unit.

#template to answer the questions

## Q x
## (a)

### Explanation

Write your explanation here.

### Code

```{r}
#Write your code here

```

### Interpretation

Explain what the output means.

------------------------------------------------------------------------

I confirm that: - I understand all code submitted. - I can explain my
solution if required.
